Paper 1 Analysis

### 2015-10-20 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Added a CR.
No reason to include Highlights.
Better appendices.
Now including a CostShare plot.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Highlights}
\label{sec:highlights}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\emph{This will go in a separate document eventually.}

\begin{itemize}
\item Highlight 1
\item Highlight 2
\item Highlight 3
\item Highlight 4
\end{itemize}

%\linenumbers

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\label{sec:conclusion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgements}
\label{sec:acknowledgements}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

>>>>

@@

<<Cost_Share_Plot, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=1.5, fig.cap="Historical cost shares for capital, labor, and energy.">>=
ggplot(
  data = gather(CostShares, key=cost_share, value=value, cs_k, cs_l, cs_e)
  ) + 
  geom_line(mapping = aes(
    x = Year, 
    y = value, 
    group = cost_share, 
    linetype = cost_share,
    color = cost_share)) +
  facet_grid( ~ Country) +
  ylab("Cost Share") +
  scale_y_continuous(limits=c(-0.2, 1.1), breaks=c(0, 0.5, 1)) +
  geom_hline(aes(yintercept = 0.3), colour="gray50", size=0.1) +
  geom_hline(aes(yintercept = 0.7), colour="gray50", size=0.1) +
  xlab("") +
  scale_x_continuous(breaks=c(1960, 1980, 2000)) +
  scale_color_manual(name = "", 
                     labels=c("k", "l", "e"),
                     values=c("black", "black", "gray70")) +
  scale_linetype_manual(name="", 
                        labels=c("k", "l", "e"),
                        values=c(2,3,1)) + 
  scale_size_manual(name="", 
                    labels=c("k", "l", "e"),
                    values = c(0.9, 0.9, 0.6)) +
  xy_theme()
@

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Fitted Graphs}
\label{sec:appendix_fitted}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Residual Graphs}
\label{sec:appendix_residual}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
